---
title: "DATA2002 Module 4 Report"
author: "Group 9 (460352996,480407614,480145820,470066919)"
output: 
  html_document:
    theme: simplex
    code_folding: hide
    toc: true
    toc_float: true
---

```{r load_packages, include=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(janitor)
library("readxl")
```

***

## 1. Introduction


The data set is adapted from th  

### 1.1 Sampling method and potential biases



### 1.2 Data import, processing and cleaning



```{r import_data, message=FALSE, warning=FALSE}
data = read_excel("infusions_data_2002.xlsx", na = c("NA"))
data = data %>% janitor::clean_names()
#glimpse(data)
```

***
## 2. Analysis
### 2.1 Body Fat

**Hypothesis**:
$$
H_0: \alpha_1 = \alpha_1 = ... = \alpha_g \\
H_1:  \text{ Not all means are the same.}\\
$$
**Assumptions:**
<ol>
<li>$\epsilon_{ijk} \sim N(0, \sigma^2)$</li>
</ol>

```{r }

```

### 2.2 Weight

**Hypothesis**:
$$
H_0: \alpha_1 = \alpha_1 = ... = \alpha_g \\
H_1:  \text{ Not all means are the same.}\\
$$
**Assumptions:**
<ol>
<li>$\epsilon_{ijk} \sim N(0, \sigma^2)$</li>
</ol>

```{r }

```

### 2.3 Body Density

**Hypothesis**:
$$
H_0: \alpha_1 = \alpha_1 = ... = \alpha_g \\
H_1:  \text{ Not all means are the same.}\\
$$
**Assumptions:**
<ol>
<li>$\epsilon_{ijk} \sim N(0, \sigma^2)$</li>
</ol>

```{r }

```

### 2.4 Age

**Hypothesis**:
$$
H_0: \alpha_1 = \alpha_1 = ... = \alpha_g \\
H_1:  \text{ Not all means are the same.}\\
$$
**Assumptions:**
<ol>
<li>$\epsilon_{ijk} \sim N(0, \sigma^2)$</li>
</ol>

```{r }

```

## 4. Limitations

## 5. Conclusion

## 6. References
<ol>
<li>  </li>
</ol> 

