---
title: "DATA2002 Module 4 Report"
author: "Group 9 (460352996,480407614,480145820,470066919)"
output: 
  html_document:
    theme: simplex
    code_folding: hide
    toc: true
    toc_float: true
---

```{r load_packages, include=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(janitor)
library("readxl")
library(ggfortify)
library(GGally)
library(qtlcharts)
library(leaps)
library(sjPlot)
library(pheatmap)
```

***

## 1. Introduction

The data set is adapted from th  

### 1.1 Sampling method and potential biases



### 1.2 Data import, processing and cleaning
```{r import_data, message=FALSE, warning=FALSE}
data = read.delim("bodyfat.txt") %>% janitor::clean_names()
data = data %>%
  mutate(bmi = (data$weight/(data$height ^ 2)) * 703,
         overweight = case_when(
          bmi >= 25 ~ 1,
          bmi < 25 ~ 0))

colnames(data)
data_bmi = data[-c(1:2,4:5,18)]
data_bf = data[-c(1,3:5,17:18)]
data_density = data[-c(2:5,17:18)]

#glimpse(data)
```

***
## 2. Analysis
### Prediction for Obesity
Due to the increasing consumptions of fast food and the increasing convenience of food deliveries, concerns about obesity level is rising throughput the world and has reached a new high. This increasing concern has lead to an increasing need to measure obesity accurately and percentage body fat is arguably the most accurate measure by far. However, the calculation of body fat is difficult and many has switched to Body Mass Index (BMI) for simpler calculation. This section is looking at comparing the results from predicting body fat percentage using other body measurements and  predicting BMI using other body measurements to determine wh body measurement is the most important in determining obesity.

#### 2.1 Body Fat Percentage
##### 2.1.1 Data Visualisation
```{r}
qtlcharts::iplotCorr(data_bf)
```
Based on the interactive correlation matrix, it can be seen the level of correlation differs quite drastically between the variables and the backward variable selection method is adopted.

##### 2.1.2 Multiple Regression
```{r}
bf_lm = lm(pct_bf~.,data=data_bf)
summary(bf_lm)
```
Using the individual p-value method, the varaibles that need to be dropped are chest, waist, thigh, knee,ankle, bicep, forearm with ankle being the first to drop down due to its high p-value. However, to double check, the AIC criterion will also be considered.

```{r}
bf_step_back = step(bf_lm, direction = "backward",trace = FALSE)
summary(bf_step_back)
```
Based on the backward selection model, the fitted model has become:

$\hat{body_fat} = 1.52 -0.3965neck - 0.128chest + 1.01805abdomen -0.28758hip + 0.26bicep -1.55084wrist $

##### 2.1.3 Check Assumptions
Finally, to check assumption, we perform the ggfortify function.
```{r}
par(mfrow=c(1,2))
plot(bf_step_back,which=1:2) + theme_bw()
```

The QQ plot shows a straight line which indicates that the normality assumption is reasonable. However, the residuals vs fitted plot shows a slight variation; but given that body fat is hard to predict, this is acceptable.

##### 2.1.4 Final fitted model
$\hat{body_fat} = 1.52 -0.3965neck - 0.128chest + 1.01805abdomen -0.28758hip + 0.26bicep -1.55084wrist $

#### 2.2 BMI
For this analysis, the formula of BMI is $BMI = \frac{Weight (lbs)*703}{Height(in)^2}$

##### 2.2.1 Data Visualisation
```{r}
qtlcharts::iplotCorr(data_bmi)
```
Based on the interactive correlation matrix, it can be seen the level of correlation differs quite drastically between the variables and the backward variable selection method is adopted.

##### 2.2.2 Multiple Regression

```{r}
bmi_lm = lm(bmi~.,data=data_bmi)
summary(bmi_lm)
```

Using the individual p-value method, the varaibles that need to be dropped are hip, ankle, bicep, forearm and wrist. To double check, the AIC criterion will also be considered.

```{r}
bmi_step_back = step(bmi_lm, direction = "backward",trace = FALSE)
summary(bmi_step_back)
```

Based on the backward selection model, the fitted model has become:

$\hat{bmi} = -10.94 +0.161chest + 0.127abdomen + 0.050hip + 0.150 thigh - 0.23knee + 0.115forearm $

##### 2.2.3 Check Assumptions
Finally, to check assumption, we perform the ggfortify function.

```{r}
par(mfrow=c(1,2))
plot(bmi_step_back,which=1:2) + theme_bw()
```

The QQ plot shows a straight line which indicates that the normality assumption is reasonable. However, the residuals vs fitted plot shows a fan shaped plot which indicates that the assumption of homogeneous variance is violated. We can use a log transformed response and re-fit the linear regression.

```{r}
ln_bmi_lm = lm(log(bmi)~.,data=data_bmi)
summary(ln_bmi_lm)
ln_bmi_step_back = step(ln_bmi_lm, direction = "backward",trace = FALSE)
summary(ln_bmi_step_back)
par(mfrow=c(1,2))
plot(ln_bmi_step_back,which=1:2) + theme_bw()
```

```{r}
sjPlot::tab_model(bmi_step_back, ln_bmi_step_back, digits = 5, show.ci = FALSE)
```

##### 2.2.4 Final Fitted Model

$log(\hat{bmi}) = 1.83 +0.0058chest + 0.0052abdomen + 0.0064 thigh -0.0065knee +        0.0028bicep + 0.0040 forearm $.


#### 2.3 Body Density
##### 2.3.1 Defining the model with population parameters
$$
Body Density = \beta_0 + \beta_1Pcf.BF + \beta_2Age + \beta_3Weight + \beta_4Height\\
+ \beta_5Neck + \beta_6Chest + \beta_7Abdomen + \beta_8Waist + \beta_9Hip + \beta_{10}Thigh\\ + \beta_{11}Knee + \beta_{12}Ankle + \beta_{13}Bicep + \beta_{14}Forearm + \beta_{15}Wrist + \epsilon
$$

```{r}
cor_matrix <- cor(data_density)
pheatmap(cor_matrix, display_numbers = T,na.rm=T)
```

Above matrix has shown the interactice correlation between variables. Notbaly, Pct.BF has a -0.99 relationship with Density, which means Pct.BF could be used to explain Density. Meanwhile, variables having similar properties are linked together, which could be useful for generating groups.

##### 2.3.2 Check Assumptions
The residuals $\epsilon_i$ are iid $N(0,\sigma^2)$ and there is a linear relationship between y and x.
```{r}
M0 <- lm(density ~ 1, data = data_density)  # Null model
M1 <- lm(density ~ ., data = data_density)  # Full model
autoplot(M1,which=1:2)+theme_bw()
round(summary(M1)$coef, 3)
```
```{r}
step.fwd.aic <- step(M0, scope = list(lower = M0, upper = M1), direction = "forward", trace = FALSE)
summary(step.fwd.aic)
step.back.aic <- step(M1, scope = list(lower = M0, upper = M1), direction = "backward", trace = FALSE)
summary(step.back.aic)
```
```{r}
exh <- regsubsets(density~., data = data_density, nvmax = 15)
plot(exh,scale="bic")
```

It is best to choose age, weight, height, neck and chest for conducting the relationship analysis with body density.

##### 2.3.3 Dropping variables using the AIC starting from the full model
```{r}


relweights <- function(fit,...){
  R <- cor(fit$model)
  nvar <- ncol(R)
  rxx <- R[2:nvar, 2:nvar]
  rxy <- R[2:nvar, 1]
  svd <- eigen(rxx)
  evec <- svd$vectors
  ev <- svd$values
  delta <- diag(sqrt(ev))
  lambda <- evec %*% delta %*% t(evec)
  lambdasq <- lambda ^ 2
  beta <- solve(lambda) %*% rxy
  rsquare <- colSums(beta ^ 2)
  rawwgt <- lambdasq %*% beta ^ 2
  import <- (rawwgt / rsquare) * 100
  import <- as.data.frame(import)
  row.names(import) <- names(fit$model[2:nvar])
  names(import) <- "Weights"
  import <- import[order(import),1, drop=FALSE]
  dotchart(import$Weights, labels=row.names(import),
           xlab="% of R-Square", pch=19,
           main="Relative Importance of Predictor Variables",
           sub=paste("Total R-Square=", round(rsquare, digits=3)),
           ...)
  return(import)
}
relweights(M3, col="blue")
```

##### 2.3.4 Fitted model for the model selected by the step-wise procedure.
$$
Body Density = 1.0746853 + 0.0011729 \times Height\\
+ 0.0012053 \times Neck + 0.004285 \times Chest\\ - 0.0020607 \times Abdomen\\
$$

Looking at the $R^2$ value (multiple R-squared) from the summary output, 71.39% of the variability of density is explained by the regression on percentage of Height, Neck, Chest, Abdomen.
<ol>
<li>On average, holding the other variables constant, a 1% increase in Height leads to a 0.0012% unit increase in Density</li>
<li>On average, holding the other variables constant, a 1% increase in Neck leads to a 0.0012% increase in Density</li>
<li>On average, holding the other variables constant, a 1% increase in Chest leads to a 0.0043% increase in Density</li>
<li>On average, holding the other variables constant, a 1% increase in Abdomen leads to a 0.0021% decrease in Density</li>
</ol>

##### 2.3.5 Linear regression assumptions for the stepwise model
```{r}
autoplot(M3,which=1:2)+theme_bw()
```

#### 2.4 Conclusion
```{r}
sjPlot::tab_model(bf_step_back, ln_bmi_step_back, digits = 5, show.ci = FALSE)
```
Through looking at the three models, we can see that using simply body measurements, it is easier to predict changes in bmi rather than percentage body fat. From the models, measurements of abdomen appears to have the greatest influence on both body fat and bmi and hence any increase should be treated with caution.

```{r}
data %>% 
  ggplot() + 
  aes(x = pct_bf, y = overweight) + 
  geom_point(size = 10, alpha = 0.1) + 
  theme_classic(base_size = 10)

glm1 = glm(overweight ~ pct_bf + bmi + density, data = data)
summary(glm1)
```


## 3. Limitations
<ol>
<li>Gender Bias</li>
<li>Privacy Issues</li>
<li>Age Range</li>
<li></li>
</ol>
## 4. Conclusion

## 5. References
<ol>
<li>  </li>
</ol> 

