---
title: "DATA2002 Module 4 Report"
author: "Group 9 (460352996,,,470066919),480145820"
output: 
  html_document:
    theme: simplex
    code_folding: hide
    toc: true
    toc_float: true
---

```{r load_packages, include=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(janitor)
library("readxl")
library(GGally)
```

***

## 1. Introduction


The data set is adapted from th  

### 1.1 Sampling method and potential biases



### 1.2 Data import, processing and cleaning



```{r import_data, message=FALSE, warning=FALSE}
data = data %>% janitor::clean_names()

```

***
## 2. Analysis
### 2.1 Prediction for Body Fat Percentage
Due to the increasing consumptions of fast food and the increasing convenience of food deliveries, concerns about obesity level is rising throughput the world and has reached a new high. This increasing concern has lead to an increasing need to measure obesity accurately and percentage body fat is arguably the most accurate measure by far. However, the calculation of body fat is difficult and many has switched to Body Mass Index (BMI) for simpler calculation. This section is looking at predicting body fat percentage using BMI and other body measurements to enable a more accurate model to determine obesity.

For this analysis, the formula of BMI is $BMI = \frac{Weight (lbs)*703}{Height(in)^2}$
#### Data import, Processing and Cleaning
```{r}
data = read.delim("bodyfat.txt")
glimpse(data)
#Introduce BMI Varaible
data=data %>% mutate(bmi=(data$Weight*703)/(data$Height^2),)
#Isolate the dataset to only contain Body Measurements and as weight and height were included in the BMI formula, it is also removed
data_bmi = data[-c(1:5)]
```

#### Data Visualisation

```{r}
ggpairs(data_bmi) + theme_bw()
```



















##### 2.4.5 Test for interaction

**Hypothesis**:
$$
H_0: \alpha_1 = \alpha_1 = ... = \alpha_g \\
H_1:  \text{ Not all means are the same.}\\
$$
**Assumptions:**
<ol>
<li>$\epsilon_{ijk} \sim N(0, \sigma^2)$</li>
</ol>

```{r }

```

## 3. Conclusion


## 4. References
<ol>
<li>  </li>
</ol> 

